### 2015-07-20 Paper1rev4/paper1rev4.tex
kk

It is important to distinguish intended action from \textit{motivation}\cite{mcclelland1985motives, rawolle2013relationships}, \textit{cost}\cite{todorov2002optimal, flash1985coordination}, or \textit{goal selection decisions}\cite{ziebart2010modeling}. In typical motor control studies, subjects are motivated to complete an experiment in a timely fashion, and are usually explicitly provided targets to reach to. Classification of intent is prevalent in both lower \cite{strausser2011development, hargrove2013robotic} and upper limb\cite{englehart2003robust, young2012improving} prosthetics where hybrid control algorithms select from among a set of discrete actions (walking/standing/flexion/extension/etc). While subjects may be \textit{motivated} to complete experiments with minimal effort/cost and their \textit{goal} may be to reach a target, here we use intent to describe the course of action (i.e., the trajectory of the arm) taken in service of goals and motives and not the goals nor the motives themselves. Particularly of interest is the intended course of action (i.e, the intended trajectory), even when the actual movement is disturbed and hence no longer matches the intent. In other words, we operationally define \textit{intent} as a subjunctive -- where would the motion have gone had it not been disturbed?

Attempts to deduce motor intent in the past have focused on the assumed spring-like properties of human muscles. Springs produce a force according to their impedance and stretch. By measuring force, impedance, and position, Gomi and Kawato\cite{gomi1997human} were able to deduce stretch and thereby infer the muscle's equilibrium point. Supporters of the ``$\lambda$ model''\cite{feldman1995origin} hypothesized that this muscle equilibrium point, and not the equilibrium of the whole arm, represented the intent of a movement even though it did not compensate for the dynamics of the arm as a feedforward controller would. Upon Gomi and Kawato's inspection of the muscle equilibrium point as it evolved in time, it was clear that it was highly complex and often not anatomically realizable. Therefore, it could not well-represent the intent of a simple reaching movement. Unlike the equilibrium point of muscle, the equilibrium point of the entire arm is the path the arm will follow in the absence of disturbance. In the presence of disturbance, the arm might be deflected from its equilibrium. It is presently unknown if or how this arm equilibrium point might change due to disturbances.

Here we propose a revised and more general method, \textit{intent extraction}, which calculates the intended trajectory even in the face of disturbances by relating environmental interaction and state to intent. The method is a class of filters that can infer the intended trajectory from the disturbance (turbulence), process (dynamic equations), actuator (muscles), and motion. The method affords new ways to study models of motor control, understand the timing and composition of intent, and how it might be altered by disturbances and injuries. Below we first present the mathematics underlying intent extraction. Then, for simplicity in this initial study, we create synthetic reaching data to examine the quality and uncertainty of this method. Finally, we demonstrate its effectiveness extracting intended action from real human reaches that have been disrupted by unpredictable disturbances. We demonstrate this effectiveness by testing the hypothesis that disturbance does not change intended action for at least 120 milliseconds. This early experiment also provides some new insights on how intended trajectories can change in reaction to disturbances.

@@

To explore the conditions under which this procedure for recovering the intent trajectory can be generalized, we take a series of steps. First, we distinguish between joint space and generalized space by introducing a generalized state variable, $x$. Second, we separate the plant (arm) into its process (dynamics), $P$, and actuator (muscles), $A$, components. Third, we model these components in a very general sense as operations,
\begin{equation} \label{eq:generalPlant}
\underbrace{\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+\overbrace{\sum_{m=1}^M A_m(x-x_e)^{(m)}}^\text{Actuator}}_\text{Plant}+E=0
\end{equation}
where $x_e$ is the equilibrium trajectory of the actuator. Fourth, we describe a  control law for the actuator using the same expansions,
\begin{equation}
\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m(x_d-x_e)^{(m)}}^\text{Actuator}=0
\end{equation}
where an internal model, $\hat{P}$ and $\hat{E}$, predicts system dynamics and external disturbances in order to determine the actuator equilibrium $x_e$ such that $x$ will track a desired path $x_d$. The feedforward component must use the actuator and hence it shares the actuator's equilibrium with the plant. This allows us to finally relate the physical system and its control law by solving for $x_e$ and substituting into \eqref{eq:generalPlant},
\begin{equation}
\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+E=\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m (x_d-x)^{(m)}}^\text{Feedback (Actuator)}
\end{equation}
wherein $x_e$ vanishes recovering our familiar model. While a proper choice of $x_e$ is perhaps essential for control, our approach does not require a model relating this equilibrium and intended trajectory. Note also that the actuator's equilibrium $x_e$ is not the process's equilibrium unless all derivatives of $x_d$ are zero.

The fact that the actuator's equilibrium $x_e$ is not the process's equilibrium is important as the actuator state ($\lambda$) has been claimed to be the intended movement\cite{feldman1995origin}. This upholds Gomi and Kawato's finding that the arm muscles' equilibrium does not represent reaching intent\cite{gomi1997human}. If the highest order coefficient of the dynamic model of the process $\hat{P}_N$ can be inverted, the impedances can be modeled, and the system is stable (e.g., the stiffness and damping are positive), it is possible to solve for $x_d^{(N)}$ and integrate for $x_d$, revealing the intended trajectory.

@@

The impedance properties of the human arm are known to be task-dependent\cite{gomi1998task}, but we need to model them in the context of our task without assuming our conclusions in the premises. To accomplish this, we fit a linear scale factor to the torque output an established model using an intermittently, unpredictably presented secondary task. This unpredictability enables us to leverage the ergodic assumption: our tasks should at least initally share the same motor plan and impedance properties. Both portions of this assumption are important. First, we fit some expectation of the motor plan, $x_d$, by using a Gaussian weighted average ($\sigma=22$ milliseconds) of each subject's hand trajectory as it evolves in time during undisturbed movement. Separate expectations were fit for each pair of movement start and end points. We then use inverse kinematics to convert these expected hand trajectories to expected joint angle trajectories, $q_d$. Taking time derivates of $q_d$ then allows us to form an expectation of the feedforward torque, $\tau_{ff}$, that will be present early in movement as in \eqref{eq:controlLaw},

@@

Simulated error due to direct parameter uncertainty (Figure 2) reached the order of millimeters and revealed particular sensitivity to mis-estimation of stiffness and changes in shoulder position from trial to trial. Direct sensitivity, which reveals the proportion of error that could be removed by correcting inaccuracy of a parameter, was an order of magnitude lower than total sensitivity, which reveals how much error would remain if all other parameters were accurate, and both implicated stiffness estimation inaccuracy as a primary cause of extraction uncertainty. Note that this sensitivity analysis does not provide information on whether models or parameter estimates are accurate, only how sensitive the model would be if they were inaccurate.

@@

The proposed approach could explain the discovery by Bizzi et al. \cite{bizzi1984posture} of a ``virtual trajectory'' ($\alpha$) in deafferented monkeys that progressed smoothly from the initial to final positions and how that virtual trajectory is different from $\lambda$, the equilibrium point of muscles -- $x_d$ and $\lambda$ are equivalent only when $x_d$ is unchanging; therefore, this muscle equilibrium cannot be the intent of a movement. By deriving the technique in a general form, we discovered that our $x_d$ is equivalent to the virtual trajectory and can be used to determine the muscle equilibrium of a $\lambda$ model.

@@

The process model does not need to be explicitly formulated. Dynamic models that strive to understand intent are wide ranging, and can include mathematical models that range in application from swarm prediction to athletic performance. The plant (such as the actions of a crowd of people or the motions of an opposing team) may be too complex to model with simple linear transformations as we present above. However, by substituting any approximation or lookup table of input-outcome tendencies, it is possible in a variety of applications to obtain the intent, even when disturbed. In other words, it may be possible to intervene before a car crashes or an opposing team scores by knowing the intent behind their action.

@@

Since trajectories were not controlled experimentally, our tests rely heavily on the assumption that disturbed intentions initially mirror undisturbed intentions. Therefore, it is not completely certain that subjects intended to move along a straight line to the target. However, this study examined straight line motions because it is well understood that people tend to repetitively attempt to reach in a straight line towards a target \cite{hodgson2000model}. Also, even when subjects are persistently perturbed by a force field, they recover their motions to a straight line with repetitive experience \cite{shadmehr1994adaptive}. Nevertheless, it may be better to employ tasks with a more specific trajectory in order to validate the intended path. Unfortunately, even such an intended trajectory may not be strictly invariant during external disturbance because some displacements may cause intent to be recalculated by the nervous system.

A key assumption in this study is that the joint impedance (stiffness) is linearly related to torque. While other approaches tend to construct paradigms that indicate or presume that the intention is static in order to derive impedance -- the so called family of system identification applications, this study makes a constrained assumption of stiffness in order to determine intent. In a sense, this approach widens the scope to include movement. Sensitivity analyses showed that approximation of stiffness is the most critical factor to accuracy in estimating intent. While serious trial-to-trial stiffness mis-estimation is unlikely, co-contraction in response to disturbance might plausibly double stiffness mid-reach. Even as the model is insensitive to normal variations, a human can halve or double their stiffness \cite{franklin2007endpoint} significantly reducing determination accuracy. This stiffening may even explain the reported deviation of intent from the baseline trajectories. Of particular concern are the large hooks at the end of the motions. These limitations may be overcome by detecting muscle co-contraction or using additional modeling assumptions to allow real-time estimation of stiffness.

The simple linear scaling of Burdet et al.'s stiffness model \cite{burdet2006stability} facilitated hypothesis testing, but was inherently limiting. More accurate approaches would provide us with many free parameters through which to determine the outcome of the eventual extraction and obtain a spurious favorable result. Like others who have examined large force disturbances, we find lower stiffnesses (our $c$ parameter) than might be expected \cite{crevecoeur2014beyond} (Table in S1 Table). This may be due to differences in tasks \cite{gomi1998task} and/or the dependency of muscle impedance on perturbation size \cite{van2010vivo}. Our results also point to the possibility of the impedance changing during motion, perhaps as a function of time.

The words \textit{intent} and \textit{equilibrium} are contentious because of the various definitions that exist in the literature. Our simple definition here is that the intent is the path that would have been taken had there been no external disturbances. A rich history of research has suggested many ways that an equilibrium trajectory can explain action through feedback responses \cite{feldman1995origin} and/or pre-planned elements \cite{shadmehr1994adaptive}. Here we suggest that one should directly define intent in the context of a hypothesized control model. Our work here assumed the model of Burdet \cite{burdet2006stability}. However, other, more sophisticated, models may be deemed more appropriate in the future. What is clear is that given some model of control, this intent extraction approach is able to invert the process to estimate intent.

It is important to mention that it is not necessary for the brain to represent intent explicitly to generate action. It is possible that the nervous system can simply learn the relationship between muscle activations and the accomplishment of goals. For example, one might simply evaluate a motion outcome and adjust descending signals to the muscles. At the same time, one may not deny the fact that there are tasks that require a explicit representation of a trajectory, such as performing a dance, drawing a picture, or conducting an orchestra. For these tasks, intent is likely represented at  some level in the nervous system. Nevertheless, the mechanics of the arm dictate the existence of an equilibrium whether intent is explicitly represented or not. Here our goal was to answer a more modest question, ``\textit{when} movement intent is a changing equilibrium, can we recover it despite external disturbances?''

@@

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgements}
Research supported by US NIH NINDS1 R01 NS053606.  We thank Felix Huang, Jagan Jimmy, Christine Massie, Tejas Madhavan, and Mohi Ahmed for their review of preliminary manuscript. We also thank the community  of the Robotics Lab at the Rehabilitation Institute of Chicago for critical commentary during the genesis of this paper and the work leading up to it.

@@

\section*{Supporting Information Legends}

\begin{description}
\item{\bf Table S1. Subject-specific parameters.} Gross body mass was self-reported. Upper arm length, forearm length, and shoulder position in the robot's coordinate system were measured \textit{in situ}. Feedback torque gain was fit as described in our methods section using the intermittently presented white noise force disturbance. This gain is relative to the total feedback torque output (stiffness, damping, and reflexes) of the model of Burdet et al.\cite{burdet2006stability}.
\end{description}

>>>>

It is not necessary for the brain to represent intent explicitly to generate action. Instead the nervous system might simply learn the relationship between muscle activations and the accomplishment of goals. For example, one might simply evaluate a motion outcome and adjust descending signals to the muscles. At the same time, one may not deny the fact that there are tasks that require an explicit representation of a trajectory, such as performing a dance, drawing a picture, or conducting an orchestra. For these tasks, intent is likely represented at some level in the nervous system. Nevertheless, the mechanics of the body dictate the existence of an equilibrium whether intent is explicitly represented or not. Here our goal was to answer a modest question, ``\textit{when} movement intent is a changing equilibrium, can we recover it despite external disturbances?''

The words \textit{intent} and \textit{equilibrium} are contentious because of the various definitions that exist in the literature (\nameref{S1_Text}). Our simple definition here is that the intent is the path that would have been taken had there been no external disturbances. We recover this intent through a mathematical procedure that only requires that intent be \textit{stable}. Two intuitive conditions need to be met:
\begin{enumerate}
\item{Action will match intent in the absence of any unexpected disturbances.}
\item{Action grows closer to intent over time following a sufficiently small disturbance.}
\end{enumerate}
When intent estimation fails, it will most often be due to the first condition. Consider a person attempting to lift Stonehenge's Heel Stone, which weighs approximately 35 tons. We could not determine how far the person intends to lift the stone as they are not strong enough to lift it at all. The second condition will seldom fail in practice as it amounts to an often-dangerous loss of control. For example, this condition fails temporarily while tripping or during a seizure. The rigidity of bone and elasticity of muscle usually ensure that this condition is met.

Dynamic models that strive to understand intent are wide ranging, and can include mathematical models that range in application from swarm prediction to athletic performance. The plant (such as the actions of a crowd of people or the motions of an opposing team) may be too complex to model with simple linear transformations as we present above. However, by substituting any approximation or lookup table of input-outcome tendencies, it is possible in a variety of applications to obtain the intent, even when disturbed. In other words, it may be possible to intervene before a car crashes or an opposing team scores by knowing the intent behind their action.

Here we propose a general method, \textit{intent extraction}, which calculates the intended trajectory even in the face of disturbances by relating environmental interaction and state to intent. The method is a class of filters that can infer the intended trajectory from the disturbance (turbulence), process (dynamic equations), actuator (muscles), and motion. The method affords new ways to study models of motor control, understand the timing and composition of intent, and how it might be altered by disturbances and injuries. Below we first present the mathematics underlying intent extraction. Then, for simplicity in this initial study, we create synthetic reaching data to examine the quality and uncertainty of this method. Finally, we demonstrate its effectiveness extracting intended action from real human reaches that have been disrupted by unpredictable disturbances. We demonstrate this effectiveness by testing the hypothesis that disturbance does not change intended action for at least 120 milliseconds. This early experiment also provides some new insights on how intended trajectories can change in reaction to disturbances.

@@

To explore the conditions under which this procedure for recovering the intent trajectory can be generalized, we take a series of steps. First, we distinguish between joint space and generalized space by introducing a generalized state variable, $x$. Second, we separate the plant (arm) into its process (dynamics), $P$, and actuator (muscles), $A$, components. Third, we model these components in a very general sense as operations,
\begin{equation} \label{eq:generalPlant}
\underbrace{\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+\overbrace{\sum_{m=1}^M A_m(x-x_e)^{(m)}}^\text{Actuator}}_\text{Plant}+E=0
\end{equation}

where $x_e$ is the equilibrium trajectory of the actuator. Fourth, we describe a control law for the actuator using the same expansions,
\begin{equation}
\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m(x_d-x_e)^{(m)}}^\text{Actuator}=0
\end{equation}
where an internal model, $\hat{P}$ and $\hat{E}$, predicts system dynamics and external disturbances in order to determine the actuator equilibrium $x_e$ such that $x$ will track a desired path $x_d$. The feedforward component must use the actuator and hence it shares the actuator's equilibrium with the plant. This allows us to finally relate the physical system and its control law by solving for $x_e$ and substituting into \eqref{eq:generalPlant},
\begin{equation}
\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+E=\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m (x_d-x)^{(m)}}^\text{Feedback (Actuator)}
\end{equation}
wherein $x_e$ vanishes recovering our familiar model. While a proper choice of $x_e$ is perhaps essential for control, our approach does not require a model relating this equilibrium and intended trajectory. Note also that the actuator's equilibrium $x_e$ is not the process's equilibrium unless all derivatives of $x_d$ are zero.

The fact that the actuator's equilibrium $x_e$ is not the process's equilibrium is important as the actuator state ($\lambda$) has been claimed to be the intended movement\cite{feldman1995origin} (\nameref{S1_Text}). This upholds Gomi and Kawato's finding that the arm muscles' equilibrium does not represent reaching intent\cite{gomi1997human}. If the highest order coefficient of the dynamic model of the process $\hat{P}_N$ can be inverted, the impedances can be modeled, and the system is stable (e.g., the stiffness and damping are positive), it is possible to solve for $x_d^{(N)}$ and integrate for $x_d$, revealing the intended trajectory.

@@

The impedance properties of the human arm are known to be task-dependent\cite{gomi1998task}, but we need to model them in the context of our task without assuming our conclusions in the premises. We intermittently and unexpectedly presented a secondary task, which we used to fit a linear scale factor to the torque output of an established model. This addresses any concern that model parameters could be tuned to favor at a particular outcome. Additionally, unpredictability enables us to leverage the ergodic assumption: our tasks should at least initially share the same motor plan and impedance properties. Both portions of this assumption are important. First, we fit some expectation of the motor plan, $x_d$, by using a Gaussian weighted average ($\sigma=22$ milliseconds) of each subject's hand trajectory as it evolves in time during undisturbed movement. Separate expectations were fit for each pair of movement start and end points. We then use inverse kinematics to convert these expected hand trajectories to expected joint angle trajectories, $q_d$. Taking time derivates of $q_d$ then allows us to form an expectation of the feedforward torque, $\tau_{ff}$, that will be present early in movement as in \eqref{eq:controlLaw},

@@

Simulated error due to direct parameter uncertainty (Figure 2) reached the order of millimeters and revealed particular sensitivity to mis-estimation of stiffness and changes in shoulder position from trial to trial. Direct sensitivity, which reveals the proportion of error that could be removed by correcting inaccuracy of a parameter, was an order of magnitude lower than total sensitivity, which reveals how much error would remain if all other parameters were accurate, and both implicated stiffness estimation inaccuracy as a primary cause of extraction uncertainty(I found this sentence pretty long and hard to comprehend). Note that this sensitivity analysis does not provide information on whether models or parameter estimates are accurate, only how sensitive the model would be if they were inaccurate.

@@

@@

@@

Since trajectories were not controlled experimentally, our tests rely heavily on the assumption that disturbed intentions initially mirror undisturbed intentions. This study examined straight line motions because it is well understood that people tend to repetitively attempt to reach in a straight line towards a target \cite{hodgson2000model}. Also, even when subjects are persistently perturbed by a force field, they recover their motions to a straight line with repetitive experience \cite{shadmehr1994adaptive}. Future studies might employ tasks with a more specific and/or explicit trajectory to facilitate comparison with the estimate intent's path. Unfortunately, even such an intended trajectory may not be strictly invariant during external disturbance because some displacements may cause intent to be recalculated by the nervous system.

Another key assumption in this study is that the joint impedance (stiffness) is linearly related to torque. While other approaches tend to construct paradigms that indicate or presume that the intention is static in order to derive impedance -- the so called family of system identification applications, this study makes a constrained assumption of stiffness in order to determine intent. In a sense, this approach widens the scope to include movement. Sensitivity analyses showed that approximation of stiffness is the most critical factor to accuracy in estimating intent. While serious trial-to-trial stiffness mis-estimation is unlikely, co-contraction in response to disturbance might plausibly double stiffness mid-reach. Even as the model is insensitive to normal variations, a human can halve or double their stiffness \cite{franklin2007endpoint} significantly reducing determination accuracy. This stiffening may even explain the reported deviation of intent from the baseline trajectories. Of particular concern are the large hooks at the end of the motions. These limitations may be overcome by detecting muscle co-contraction or using additional modeling assumptions to allow real-time estimation of stiffness.

The simple linear scaling of Burdet et al.'s stiffness model \cite{burdet2006stability} facilitated hypothesis testing, but was inherently limiting. More accurate approaches would provide us with many free parameters through which to determine the outcome of the eventual extraction and obtain a spurious favorable result. Like others who have examined large force disturbances, we find lower stiffnesses (our $c$ parameter) than might be expected \cite{crevecoeur2014beyond} (\nameref{S1_Table}). Differences in tasks studied \cite{gomi1998task} and/or the dependency of muscle impedance on perturbation size \cite{van2010vivo} may explain this stiffness reduction. Our results also point to the possibility of the impedance changing during motion, perhaps as a function of time.

@@

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgements}
Research supported by US NIH NINDS1 R01 NS053606.  We thank Felix Huang, Jagan Jimmy, Christine Massie, Tejas Madhavan, Mohi Ahmed, and Yazan Abdel Majeed for their review of preliminary manuscript. We also thank the community  of the Robotics Lab at the Rehabilitation Institute of Chicago for critical commentary during the genesis of this paper and the work leading up to it.

@@

\section*{Supporting Information}

\subsection*{S1 Table}
\label{S1_Table}
{\bf Subject-specific parameters.} Gross body mass was self-reported. Upper arm length, forearm length, and shoulder position in the robot's coordinate system were measured \textit{in situ}. Feedback torque gain was fit as described in our methods section using the intermittently presented white noise force disturbance. This gain is relative to the total feedback torque output (stiffness, damping, and reflexes) of the model of Burdet et al.\cite{burdet2006stability}.

\subsection*{S1 Text}
\label{S1_Text}
{\bf What intent is not.} It is important to distinguish intended action from \textit{motivation}\cite{mcclelland1985motives, rawolle2013relationships}, \textit{cost}\cite{todorov2002optimal, flash1985coordination}, or \textit{goal selection decisions}\cite{ziebart2010modeling}. In typical motor control studies, subjects are motivated to complete an experiment in a timely fashion, and are usually explicitly provided targets to reach to. Classification of intent is prevalent in both lower \cite{strausser2011development, hargrove2013robotic} and upper limb\cite{englehart2003robust, young2012improving} prosthetics where hybrid control algorithms select from among a set of discrete actions (walking/standing/flexion/extension/etc). While subjects may be \textit{motivated} to complete experiments with minimal effort/cost and their \textit{goal} may be to reach a target, here we use intent to describe the course of action (i.e., the trajectory of the arm) taken in service of goals and motives and not the goals nor the motives themselves. Particularly of interest is the intended course of action (i.e, the intended trajectory), even when the actual movement is disturbed and hence no longer matches the intent. In other words, we operationally define \textit{intent} as a subjunctive -- where would the motion have gone had it not been disturbed?

Attempts to deduce motor intent in the past have focused on the assumed spring-like properties of human muscles. Springs produce a force according to their impedance and stretch. By measuring force, impedance, and position, Gomi and Kawato\cite{gomi1997human} were able to deduce stretch and thereby infer the muscle's equilibrium point. Supporters of the ``$\lambda$ model''\cite{feldman1995origin} hypothesized that this muscle equilibrium point, and not the equilibrium of the whole arm, represented the intent of a movement even though it did not compensate for the dynamics of the arm as a feedforward controller would. Upon Gomi and Kawato's inspection of the muscle equilibrium point as it evolved in time, it was clear that it was highly complex and often not anatomically realizable. Therefore, it could not well-represent the intent of a simple reaching movement. Unlike the equilibrium point of muscle, the a pre-planned equilibrium point of the entire arm is the path the arm will follow in the absence of disturbance \cite{shadmehr1994adaptive}. In the presence of disturbance, the arm might be deflected from its equilibrium. It is presently unknown if or how this arm equilibrium point might change due to disturbances.

The proposed approach could explain the discovery by Bizzi et al. \cite{bizzi1984posture} of a ``virtual trajectory'' ($\alpha$) in deafferented monkeys that progressed smoothly from the initial to final positions and how that virtual trajectory is different from $\lambda$, the equilibrium point of muscles -- intent and $\lambda$ are equivalent only when intent is unchanging; therefore, this muscle equilibrium cannot be the intent of a movement. By deriving the technique in a general form, we discovered that our intent is equivalent to the virtual trajectory and can be used to determine the muscle equilibrium of a $\lambda$ model.
